Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-14 paper/tex/introduction.tex
macros

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability $p(z)$ as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

@@

This paper is distinguished by its focus on the evaluation criteria for \pzpdf s and interpretation thereof, as a key project of the Photometric Redshift working group of the \lsstdesc\ that aims to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to select those that will become part of the \lsst\ pipelines, as laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.

>>>>

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

@@

This paper is distinguished by its focus on the evaluation criteria for \pzpdf s and interpretation thereof, as a key project of the Photometric Redshifts working group of the \lsstdesc\ that aims to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to ultimately select those that will become part of the \lsst\ pipelines, as laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.
